---
title: "Regression Model"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About the Data Set
### Description
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).
### Format
A data frame with 32 observations on 11 (numeric) variables.

[, 1]	mpg	Miles/(US) gallon

[, 2]	cyl	Number of cylinders

[, 3]	disp	Displacement (cu.in.)

[, 4]	hp	Gross horsepower

[, 5]	drat	Rear axle ratio

[, 6]	wt	Weight (1000 lbs)

[, 7]	qsec	1/4 mile time

[, 8]	vs	Engine (0 = V-shaped, 1 = straight)

[, 9]	am	Transmission (0 = automatic, 1 = manual)

[,10]	gear	Number of forward gears

[,11]	carb	Number of carburetors


### Load and scan the data
```{r cars}
data(mtcars)
summary(mtcars)
str(mtcars)
head(mtcars)
```

### Check the difference within the transmossion. 
```{r compare}
## t test
t.test(mtcars[mtcars$am == 0,]$mpg, mtcars[mtcars$am==1,]$mpg)
## boxplot
library(ggplot2)
mtcars$trans = mtcars$am
mtcars[mtcars$am == 0,]$trans = "Auto"
mtcars[mtcars$am == 1,]$trans = "Manual"
ggplot(data = mtcars, aes(factor(trans),mpg)) + 
  geom_boxplot() + 
  labs(x = 'Transmission', y = "MPG", title = "MPG based on Auto and Manual")
```

### Check the difference within the transmossion. 
```{r diff}
## t test
t.test(mtcars[mtcars$am == 0,]$mpg, mtcars[mtcars$am==1,]$mpg)
## boxplot
library(ggplot2)
mtcars$trans = mtcars$am
mtcars[mtcars$am == 0,]$trans = "Auto"
mtcars[mtcars$am == 1,]$trans = "Manual"
ggplot(data = mtcars, aes(factor(trans),mpg)) + 
  geom_boxplot() + 
  labs(x = 'Transmission', y = "MPG", title = "MPG based on Auto and Manual")
```

From the t-test, we can find that the p value is less than 0.05, so we reject the null hyothesis that there are no difference between the twp group. And we can also drive the conclusion from the plot.

### An aerial view of the correlations between pairs of variables.

```{r view}
## t test
mtcars$trans = NULL

pairs(mtcars, panel = panel.smooth)
library(corrgram)
corrgram(mtcars, lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         main="Car Milage Data in PC2/PC1 Order")

library(corrplot)
corrplot(cor(mtcars), method = "ellipse")
```

Transfer the categorical data to factor
```{r category}
for (i in c('cyl', 'vs', 'am', 'gear', 'carb')){
  mtcars[,i] = factor(mtcars[,i])
}
```

### Begin the dealing the data from the all in one, and then use the stepwise regression. Varicance inflation factor is utilized in reviewing the variables.

#### 1st All in model
```{r allin}
allin = lm(data = mtcars, mpg ~ .)
summary(allin)
library(car)
vif(allin)
```

We find in the all-in data, no variable is significant and there are variables with huge VIFs. So, we have to modified the regression model.
#### Modifying Process

```{r modify}
modified1 = update(allin, mpg ~ cyl+disp+hp+drat+wt+qsec+vs+am+gear)
summary(modified1)
vif(modified1)
modified2 = update(allin, mpg ~ disp+hp+drat+wt+qsec+vs+am+gear)
summary(modified2)
vif(modified2)
modified3 = update(allin, mpg ~ hp+drat+wt+qsec+vs+am+gear)
summary(modified3)
vif(modified3)
modified4 = update(allin, mpg ~ hp+drat+wt+qsec+vs+am)
summary(modified4)
modified5 = update(allin, mpg ~ hp+drat+wt+qsec+am)
summary(modified5)
modified6 = update(allin, mpg ~ hp+wt+qsec+am)
summary(modified6)
modified7 = update(allin, mpg ~ (wt+qsec)*am)
summary(modified7)
modified8 = update(allin, mpg ~ wt*am+qsec)
summary(modified8)
```

After 8th try, we find the finally successful model which contains intersection variable. 

#### check the Final modified model.

Utilized the regsubsets function to check whether the finally modified model with the best selected independent variables.

```{r check}
library(leaps)
check <- regsubsets(mpg ~ ., data = mtcars)
summary(check)
plot(check, scale = "Cp")
abline(h = 8, col = "red", lwd = 3)
```

Same variables selected as the stepwise regression process.

#### Plots to show the correlations

```{r plotshow}
mean(modified8$residuals)
var(modified8$residuals)
par(mfrow = c(2, 2))
plot(modified8)
```

We checked the mean of the residuals, which is almost zero. And there is no patterns to conclude in the residuals plots, except that the QQ plot does not show a perfect normal distribution.